SIR Model with Testing and Isolation Mechanisms

### 2020-11-10 codes/ali_test_sir.Rmd
updated notes

### Contour plot of $R_0=1$ and interpretations approache 1
```{r contour_R0_1, message=FALSE,warning=FALSE }
n_out <- 5 ## facets (rows/cols)
n_in <- 41 ## grid N within facets
 # specify the ranges
 beta  <- 0.339  ## set beta high enough to allow R0>1 in worst case
 eta_w <- seq(0,1, length.out=n_out)
 eta_t <- seq(0,1, length.out=n_out) #0.001 to 0.5 
 rho     <- seq(0,0.01, length.out=n_in)
 omega <- seq(0.1,2 , length.out=n_in) #note omega must be > rho, was 0.011
 W_S <- 0.3 #choose 0.3 for TTI testing plan and 1 for the random testing.

@@

```{r show_contours_2, width=24,height=24,message=FALSE,warning=FALSE}
p11 <- ggplot(df22,aes(x=omega,y=rho,z=R0))+ theme_bw() +
    theme(panel.spacing=grid::unit(0,"lines"))
(p11
    + geom_contour_filled(breaks=pretty(unique(df22$R0),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(s~eta_t, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"))
    + ggtitle("W[S]=0.3, W[I]=W[R]=1")
)
```

>>>>

### Contour plot of $R_0=1$ and interpretations approache 1
```{r contour_R0_1, message=FALSE,warning=FALSE }
n_out <- 5 ## facets (rows/cols)
n_in <- 41 ## grid N within facets
 # specify the ranges
 beta  <- 0.339  ## set beta high enough to allow R0>1 in worst case
 eta_w <- seq(0,1, length.out=n_out)
 eta_t <- seq(0,1, length.out=n_out) #0.001 to 0.5 
 rho     <- seq(0,0.01, length.out=n_in)
 omega <- seq(0.1,2 , length.out=n_in) #note omega must be > rho, was 0.011
 W_S <- 1 #choose 0.3 for TTI testing plan and 1 for the random testing.

@@

```{r show_contours_2, width=24,height=24,message=FALSE,warning=FALSE}
p11 <- ggplot(df22,aes(x=omega,y=rho,z=R0))+ theme_bw() +
    theme(panel.spacing=grid::unit(0,"lines"))
p2_temp <- (p11
    + geom_contour_filled(breaks=pretty(unique(df22$R0),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(s~eta_t, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"))
    + ggtitle("W[S]=1, W[I]=W[R]=1")
)
p2_temp
ggsave(p2_temp,filename = "R0contour_random_s.png" , path="../pix/")
```

### 2020-11-10 note/SIR_notes.Rnw
updated notes

\documentclass{article}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{subcaption}
\bibliographystyle{apalike}

@@

% %%%%%%%
\section{Method}
- $\Lambda$: force of infection defined as $$\Lambda=\beta \frac{(I_u+\eta_w I_n+\eta_w I_p+ \eta_t I_t)}{N_0},$$ where $\beta$ is transmission rate, $\eta_w$ and $\eta_t$ are the isolation parameters for awaiting and reported individuals, respectively. We assume that $\eta_t<\eta_w$, i.e., the awaiting individuals for test results have a higher transmission probability than the reported individuals.
- $\omega$: the rate of *onward flow* from the awaiting positive compartment, $p$, to reported/tested compartment, $\rho$, or from awaiting negative compartment, $n$, back to $u$.  It has units of $1/time$.
- $\gamma$: recovery rate ($1/time$).
- $\rho$: per capita testing intensity across the whole population ($1/time$).
- $W$: weighted number of people available for tests, defined as $W = W_S S_u + W_I I_u + W_R R_u$.
- $\sigma$: scaling parameter for testing defined as $\sigma = \frac{\rho N_0}{W}$.
- $F_Z$: Weighted testing rate defined as $F_Z=\sigma W_Z$. That is, $F_S = \sigma W_S$, $F_I=\sigma W_I$ and $F_R = \sigma W_R$.

@@

@@

@@

\begin{enumerate}
\item aa
\end{enumerate}

>>>>

\documentclass{article}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath}
\bibliographystyle{apalike}

@@

% %%%%%%%
\section{Method}

\subsection{model and parameters}
\begin{itemize}
\item $\Lambda$: force of infection defined as $$\Lambda=\beta \frac{(I_u+\eta_w I_n+\eta_w I_p+ \eta_t I_t)}{N_0},$$ where $\beta$ is transmission rate, $\eta_w$ and $\eta_t$ are the isolation parameters for awaiting and reported individuals, respectively. We assume that $\eta_t<\eta_w$, i.e., the awaiting individuals for test results have a higher transmission probability than the reported individuals.
\item $\omega$: the rate of *onward flow* from the awaiting positive compartment, $p$, to reported/tested compartment, $\rho$, or from awaiting negative compartment, $n$, back to $u$.  It has units of $1/time$.
\item $\gamma$: recovery rate ($1/time$).
\item $\rho$: per capita testing intensity across the whole population ($1/time$).
\item $W$: weighted number of people available for tests, defined as $W = W_S S_u + W_I I_u + W_R R_u$.
\item $\sigma$: scaling parameter for testing defined as $\sigma = \frac{\rho N_0}{W}$.
\item $F_Z$: Weighted testing rate defined as $F_Z=\sigma W_Z$. That is, $F_S = \sigma W_S$, $F_I=\sigma W_I$ and $F_R = \sigma W_R$.
\end{itemize}

@@

The model is

\begin{align}
\label{mod:1}
 d S_u/dt &= -\Lambda S_u - F_S S_u + \omega S_n \\
 d S_n/dt &= -\Lambda S_n + F_S S_u - \omega S_n \\
 d I_u/dt &= \Lambda S_u - F_I I_u + \omega I_n  - \gamma I_u  \\
 d I_n/dt &= \Lambda S_n + (1-p_I) F_I I_u - \omega I_n -\gamma I_n \\
 d I_p/dt &= p_I F_I I_u - \omega I_p -\gamma I_p \\
 d I_t/dt &= \omega I_p - \gamma I_t  \\
 d R_u/dt &= \gamma I_u - F_R R_u + \omega R_n \\
 d R_n/dt &= \gamma I_n + (1-p_R) F_R R_u - \omega R_n  \\
 d R_p/dt &= \gamma I_p + p_R F_R R_u  - \omega R_p  \\
 d R_t/dt&= \gamma I_t + \omega R_p  \\
 dN/dt &= \omega (S_n + I_n + R_n)   \\
 dP/dt &= \omega(I_p + R_p).
\end{align}

@@

\begin{figure}
\centering
\begin{subfigure}[t]{.45\textwidth}
\centering
\includegraphics[width=\linewidth]{../pix/R0contour_random_s.png}
        \caption{}\label{fig:fig_a}
\end{subfigure}
%
\begin{subfigure}[t]{.45\textwidth}
\centering
\includegraphics[width=\linewidth]{../pix/R0contour_TTI_s.png}
\caption{}\label{fig:fig_b}
\end{subfigure}
\end{figure}

@@

\begin{enumerate}
\item 
\begin{itemize}
\item analysis of the basic SIR model with testing: analytical results as far as possible, supplemented by numerical results as necessary/for illustration. Heuristic explanations/insights of what we learn from this.
\item Maybe?? order-of-magnitude/back-of-the-envelope calculations of the magnitudes of testing and isolation necessary. (However, the model may be too simplified for even back-of-the-envelope calculations to be meaningful.)
\item Maybe?? comparison with strength-and-speed framework (since T/T/I is essentially a speed-based intervention)
\end{itemize}

\item
\begin{itemize}
\item extension to a SEPAIR model (i.e. including latent/exposed, presymptomatic, asymptomatic)
  (i) analytical results will probably be out of reach
	(ii) but it may be possible to extend some of the insights gained in part 1
	(iii) in any case, some numerical results (the space of relevant/interesting parameters will be larger: figure out a sensible way to show results from this parameter space. Are there useful dimensionless parameters that could help frame this?)
\item more detailed quantitative exploration: in particular, *either* Latin hypercube *or* (nearly the same!) a sample over estimated ('prior') distributions of the parameters. Goal: answer the general question "how likely is TTI to be able to control COVID?"
\end{itemize}
\end{enumerate}

% \item extension to a SEPAIR model (i.e. including latent/exposed, presymptomatic, asymptomatic)
%     * analytical results will probably be out of reach
% 	* but it _may_ be possible to extend some of the insights gained in part 1
% 	* in any case, some numerical results (the space of relevant/interesting parameters will be larger: figure out a sensible way to show results from this parameter space. Are there useful dimensionless parameters that could help frame this?)
% \item more detailed quantitative exploration: in particular, *either* Latin hypercube *or* (nearly the same!) a sample over estimated ('prior') distributions of the parameters. Goal: answer the general question "how likely is TTI to be able to control COVID?"
